Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2023-02-22 Edith Zemanick/Sweat Test/sweat_test_analysis.Rmd
swaet test updates done

```{r}

```

@@

For all participants with more than one sweat test, we compared their first and last values.

```{r results='asis'}
# Get first and last values for everyone with more than 1
multiples <- df %>%
  group_by(PatientID) %>%
  filter(n() > 1) %>% # Multiple values only
  filter(row_number() == 1 | row_number() == n()) %>% # First and last
  mutate(time = row_number())
multiples$time <- factor(multiples$time, levels = 1:2, labels = c("First", "Last"))
# Paired testing options
mycontrols <- tableby.control(
  numeric.test = "signed.rank", cat.test = "mcnemar",
  numeric.stats = c("Nmiss", "median", "q1q3")
)
```

```{r results='asis'}
p <- paired(
  time ~ Cl + Na + `Na/Cl Ratio`,
  signed.rank.exact = F, data = multiples,
  id = PatientID, control = mycontrols
)
summary(p, pfootnote = T, labelTranslations = labels)
```

>>>>

For all participants with more than one sweat test, we used only their first value to calculate the absolute difference (AD) between left and right arm.

```{r}
t1_df$`Cl AD` = abs(t1_df$Cl_Left-t1_df$Cl_Right)
t1_df$`Na AD` = abs(t1_df$Na_Left-t1_df$Na_Right)
```

### By diagnosis

```{r results='asis'}
t1 <- tableby(
  Diagnosis ~ `Cl AD`+`Na AD`,
  data = t1_df, control = mycontrols,
)
summary(t1,
  pfootnote = T,
  labelTranslations = labels
)
```

### By sweat chloride group

```{r results='asis'}
t1 <- tableby(
  `Sweat Chloride Group` ~ `Cl AD`+`Na AD`,
  data = t1_df, control = mycontrols
)
summary(t1,
  pfootnote = T,
  labelTranslations = labels
)
```

### By genotype risk

```{r results='asis'}
t1 <- tableby(
  geno_risk ~ `Cl AD`+`Na AD`,
  data = t1_df, control = mycontrols
)
summary(t1,
  pfootnote = T,
  labelTranslations = labels
)
```

@@

For all participants with more than one sweat test, we compared their first and last values by calculating the absolute difference (AD) between first and last measure.

```{r results='asis'}
# Get first and last values for everyone with more than 1
multiples <- df %>%
  group_by(PatientID) %>%
  filter(n() > 1) %>% # Multiple values only
  filter(row_number() == 1 | row_number() == n()) %>% # First and last
  summarise(`Cl AD` = abs(last(Cl) - first(Cl)), # Calculate AD
            `Na AD` = abs(last(Na) - first(Na)),
            Diagnosis = first(Diagnosis),
            `Sweat Chloride Group` = first(`Sweat Chloride Group`),
            geno_risk = first(geno_risk)) 
```

### By diagnosis

```{r results='asis'}
t1 <- tableby(
  Diagnosis ~ `Cl AD`+`Na AD`,
  data = multiples, control = mycontrols,
)
summary(t1,
  pfootnote = T,
  labelTranslations = labels
)
```

### By sweat chloride group

```{r results='asis'}
t1 <- tableby(
  `Sweat Chloride Group` ~ `Cl AD`+`Na AD`,
  data = multiples, control = mycontrols
)
summary(t1,
  pfootnote = T,
  labelTranslations = labels
)
```

### By genotype risk

```{r results='asis'}
t1 <- tableby(
  geno_risk ~ `Cl AD`+`Na AD`,
  data = multiples, control = mycontrols
)
summary(t1,
  pfootnote = T,
  labelTranslations = labels
)
```
